Equations & R Code

### 2016-09-29 manuscript/coexistence-stability_ms.Rmd
updates final conceptual figure and adds to ms

---
layout: 12pt
header-includes:
  - \usepackage{lineno}
  - \linenumbers
  - \usepackage{setspace}
  - \usepackage{todonotes}
  - \doublespacing
  - \usepackage{rotating}
  - \usepackage{color, soul}
  - \usepackage[font={footnotesize},labelfont=bf,labelsep=space]{caption}
  - \usepackage{times} 
  - \usepackage{sectsty}
bibliography: ~/Dropbox/Bibliography/CoexistStability.bib
csl: components/ecology.csl

@@

>>>>

---
layout: 12pt
header-includes:
  - \usepackage{lineno}
  - \linenumbers
  - \usepackage{setspace}
  - \usepackage{todonotes}
  - \doublespacing
  - \usepackage{rotating}
  - \usepackage{color, soul}
  - \usepackage[font={footnotesize},labelfont={sf,bf},labelsep=space]{caption}
  - \usepackage{times} 
  - \usepackage{sectsty}
bibliography: ~/Dropbox/Bibliography/CoexistStability.bib
csl: components/ecology.csl

@@

\begin{figure}[!ht]
  \centering
      \includegraphics[height=4in]{./components/coexistence_stability_infographic_v2.png}
  \caption{Example of how species additions under increasing environmental variability can buffer ecosystem stability when species coexistence is fluctuation-dependent via the storage effect. Environmental variability ($\sigma^2_E$) increases linearly with time. (a) Time series of total community biomass in a closed community where colonization of new species is not possible and (b) its associated coefficient of variation (Rolling CV; calculated over 100-yr moving window) through time. (c) Time series of total community biomass (dark purple) and constituent species (other, semi-transparent colors) in an open community where colonization by new species from the regional pool of 4 species becomes possible as environmental variation increases. The trajectory of total biomass CV in the open community (d) asymptotes at lower variability than in the closed community (b) due to the buffering effect of species richness.}
\end{figure}
